Hemodynamic responses of the Parahippocampal Place Area to spatial cues in a movie and its audio-description

### 2020-08-05 paper/main.tex
some more structure for discussion

\todo[inline]{taylor it to points mentioned in the introduction (full circle)}

\paragrap{intro}
We used two naturalistic stimuli + annotation + GLM and investigated if we could
isolate the PPA not just in an group average analysis but also on an individual
level. We focus on the audio-only stimulus but performed a analysis for the AV
stimulus as well (not controlling for frame content after cuts).

% Correlation of regressors
Events/Regressors are of little to no correlation despite stimulus was used as
designed for entertainment purposes.

\subsection{Group analysis}

% AO stimulus
% cluster location
AO stimulus isolated spatially concise cluster in anterior part of group overlap mask/roi.
% confounds
2h audio-description offering sufficient events such that many confounding
variables average out (but some anternative contrasts show clusters in auditory
cortices)
% summary statement
This suggest spoken language cues correlate with increased activation in higher
visual areas bilaterally.

% RSC
words to clusters in RSC? -> see Aminoff (20xx). What does the retrosplenial
cortex do?

% theory what the PPA does
\todo[inline]{aminoff2013: jedoch zu non-spatial stuff: Although the PHC is
commonly thought of as responding to visual stimuli, it has also been found to
elicit activity for auditory stimuli [25,26,30,31] and to respond to odor
stimuli [32–34].}
% Mental Imagery Hypothesis
Mental Imagery Hypthesis (s. O'Craven \& Kanwisher, 2000); Lerner (2011), Honey
(2012), Silbert (2014) finden keine ISC in PPA? vgl. auch DataPaper bzgl.
Hörbuch??
% we
We got not task not time to form a vivid mental image; if at all automatic
on-the-fly process; further not task to keep subjects attentive to the stimulus
and espcially spatial cues
% PPA is not visual exclusively
results of other studies suggest7 the PPA does not exclusively process the
``spatial layout''" but ``contextual associations''.
% difference to Aziz
Aziz modeled as boxcar from sentence onset to offset.

% AV stimulus cluster location
AV middle and posterior part of group overlap mask/roi.
% confounds
extending into more posterior regions (which exactly?).
% not controlled frame content
putativ function of those regions?
% number of events?
confounds to not average out in (early) visual areas.
% nevertheless
imo it's cool, that this approach of blindly averaging the frames' content works
at all.

@@

\subsection{individual analyses}
% AO
We were able to get isolated cluster in anterior part of individual PPA masks in
majority of subjects.
% one threshold for all
Same threshold for all subjects, PPA ROIs were visually / subjectively chosen.
% inter-individual differences
\todo[inline]{which contrasts work better in some subjects?}
% sub-xy
AO yielded bilateral cluster whereas AV stimulus yielded XY and even the
dedicated localizer yieled just one unilateral custer.

% summary statement
Results suggest naturalistic AO stimulus can be used as an non-visual localizer
of a visual area in individual subjects.
% with other words
a  complex auditory stimulus might allow individual localization of a
functionally defined brain region.
% and again other words
an audio drama might be suitable as ecologically more valid ``localizer'' for a
variety of brain functions.
% other example: speech areale
other possibilities: low level features, stuff annotated in speech annotation

% multiple localizer
% PPA is just one example
2h stimulus for just one process is long but chosen cognitive function is just
one aspect that can be investigated with a complex naturalistic stimulus.

% AV
On individual level, mixed results for AV stimulus.
% individual differences
Individual differences when seeing a whole picture with many features vs.
serialc auditory stream of information providing incidential cues; spatial attention?
\todo[inline]{which contrast works better in which subjects?}

% AO vs. AV
AO vs. AV\dots
\todo[inline]{Hanke et al. (2014): Compared to an audio-visual movie, this is a
    stimulus that leaves a much larger margin for inter-individual differences
    in imagining scenery, as well as actors' character and personality traits,
    while still preserving the time-locked presentation of information to a
    listener. At the same time, an auditory stimulus limits the effect of an
    attentional focus on the selection of a subset of simultaneously occurring
    auditory events, in contrast to the selection of different parts of the
visual field}.

\subsection{shortcomings}

% spatial cues can belong to different categories
setting\_new ist häufig vermischt mit anderer Kategorie "ein Arzt", "ein alter
Film", "auf einer Straße", "im Fernsehen", "die drei Jungs", "die zwei im Bett",
"Jenny als Teenager", "Forrest vor einem Buffet", "Kennedy", "Jenny kommt aus
dem Wohnwagen ihrer Großmutter"
% soundsscapes makes change of setting obvious before narrator kicks in
Soundscape macht es häufiger bereits vorher klar, dass Settingwechsel ist bzw.
nicht erst das annotiere Substantiv object und (room)geo ist vermischt
Retrospelinal Cortex ist in Probabilistic maps krasser als PPA.

@@

\subsection{open question: anterior (AO) vs. posterior (AV) PPA}

\subsection{model-driven vs. data-driven analyses} Due to their continuity,
complexity, and length, they offer a vast amount of data on a variety of brain
functions like low-level perception, attention, comprehension, memory, emotions,
or social interactions. This suggests the data can later be reused for variety
of totally different, independent research questions, possibly on an individual
level.

\subsection{confounds in AO and AV}

\subsection{re-use of existing data for new, independent research questions}
there is more in a complex naturalistic stimulus.

Natural stimuli like movies \citep{hasson2008neurocinematics,
sonkusare2019naturalistic} or narratives \citep{honey2012not,
lerner2011topographic, silbert2014coupled} offer an easy to implement,
(continuous,) complex, immersive, task-free paradigm that more closely resembles
our natural dynamic environment than traditional experimental designs.

@@

\subsection*{Code availability}
% wo kommt dieser Abschnitt hin?
% how to write Code availability statement
% https://www.springernature.com/gp/authors/research-data-policy/data-availability-statements/12330880
\todo[inline]{provide supporting source code, and explaining how and where others may access all data underlying the analysis}
\emph{for all studies using custom code in the generation or processing of datasets,
a statement must be included here, indicating whether and how the code can be
accessed, including any restrictions to access; include information on the versions
of any software used, if relevant, and any specific variables or parameters used to
generate, test, or process the current dataset. }

>>>>

\todo[inline]{tailor it to points mentioned in the introduction (full circle);
print intro to avoid constant scrolling}

\subsection{intro}
\todo[inline]{summary of study goal and methods}
% what we did
We used two naturalistic stimuli and their annotations to create a GLM
presumably correlating with hemodynamic activity in the PPA. We focused on the
AO stimulus but also build contrasts for the AV stimulus for cross-modal
control.

\subsubsection{correlation of regressors} Both stimuli were not designed to
maximize detection power in an fMRI experiment bu to entertain the audience.
% why we created the correlation matrix in the first place
We tested for correlation of stimulus features because a high degree of shared
variance prevents detection power.
% summary of results
Results show only minor to no correlations of regressors across all stimulus
segments
% statement
Hence depending on the stimulus features of interest, it is feasible to use
specific stimulus features of a regular movie or audiobook for neuroscientific
research questions.

\subsection{group analysis}

\subsubsection{AO stimulus}
% AO stimulus cluster location
The results of the AO stimulus yielded isolated clusters in the anterior part of
the PPA ROI (overlap of individual PPAs taken from Sengupta et al.).
% comparison to other studies using ISC
\todo[inline]{check Wilson (2008), Lerner (2011), Honey (2012), Silbert (2014).
Do they find ISC in PPA using an auditory stimulus? As far as I remember they
don't}
% diff to Aziz (2008)
Unlike \citep{aziz2008modulation} we did not use whole sentences as events to
model a hemodynamic response but the length of the word giving the cue about the
visual content of a scene.
% no task
Compared to previous studies (O'Craven \& Kanwisher: mental imagery
hypothesis)\todo{check this paper out} participants of our study were not
instructed to form a vivid mental image of the stimulus but to ``enjoy the
audiobook''.
% naive to the research question
Moreover, participants could not infer the perceptual process to be investigated
by merely being submitted to the stimuli / experimental design.
% concluding statement
This suggest the PPA is involved in processing incidental spatial information
embedded in a rich auditory stream, and this involvement does not rely on
creating a mental imagery or deliberately paying close attention to spatial
features.\todo{kinda similar to Wolbers (2011) who checked connectivity between
    PPA and visual cortex during haptic exploration of LEGO scenes}

% other
\todo[inline]{Aminoff (2013). PPA's role in cognition regarding non-spatial
    stuff: ``Although the PHC is commonly thought of as responding to visual
    stimuli, it has also been found to elicit activity for auditory stimuli
    [25,26,30,31] and to respond to odor stimuli [32–34]''.}
% concluding statement
In summary, our group results suggest that auditory spatial information does not
just modulate activity in the PPA (depending on other factory like familiarity,
XY; s. Aziz) but correlates with bilaterally increased
activation.\todo{``modulate'' suggests causation}

\subsubsection{AV stimulus}

% location
AV anterior, middle and posterior part of group overlap mask/roi.

% difference in location/size to AO und VIS
extending into more posterior regions; which exactly; known functions of theses
areas
% shortcomings + explanation
shortcoming of not controlling visual content of the frames after the cut;
% but
nevertheless it's ``surprising'' that it works at all and the clusters located
in systematically / bilaterally in (higher) visual areas; lot's of (non) visual
features average out; and we are not using a dedicated stimulus
% what should be done to improve
make an annotation of frame's content

\subsubsection{open question anterior vs. posterior PPA???}

\subsubsection{Retrosplenial cortex}
\todo[inline]{check location in primary contrast and in overlap of contrasts;
atlases do not ``know'' RSC as such but provide other term(s)}
\todo[inline]{cf. Aminoff (20xx). What does the retrosplenial cortex do?}
Another region that showed significantly increased activity not just in the
primary contrast but consistently across contrasts is ventral precuneus / RSC
(check the overlap again to not talk shit; no atlas gives RSC as such)\dots

\subsection{individual analyses}

\subsubsection{AO stimulus}
% intro
Contrast 1 yielded isolated cluster in the anterior part of individual PPA masks
in majority of subjects.
% one threshold for all
Contrary to Sengupta et al. (2016) results were archieved by using the same
Z-value and significance threshold for all subjects, and not by visually
expecting the results and choosing a subjectively best fitting threshold for
each subject.
\todo[inline]{what about the info in Bland-Altman-Plots; discussion of that info
could range from 2 sentences to 2 paragraphs}
% inter-individual differences
\todo[inline]{which contrasts work better in some subjects?}
% AO stimulus vs. AV stimulus
\todo[inline]{Hanke et al. (2014): Compared to an audio-visual movie, this is a
    stimulus that leaves a much larger margin for inter-individual differences
    in imagining scenery, as well as actors' character and personality traits,
    while still preserving the time-locked presentation of information to a
    listener. At the same time, an auditory stimulus limits the effect of an
    attentional focus on the selection of a subset of simultaneously occurring
    auditory events, in contrast to the selection of different parts of the
visual field}.
% sub-xy
AO yielded bilateral cluster whereas AV stimulus yielded XY and even the
dedicated localizer yieled just one unilateral custer.\todo{what to do with
that?}
% summary statement group results a representative for group
The individual results suggest that the group results are not driven by a couple
of subjects.
% auditory localizer
Moreover, a complex but naturally engaging auditory stimulus like an audiobook
might in principle be used as a non-visual localizer for a variety of brain
functions in subjects who are not willing or able to follow task instructions
during brain scanning.
% PPA just an example
The feature ``auditory spatial information'' is just one
example of a stimulus feature that can be annotated and used to build a model.

\subsubsection{AV stimulus}
On individual level, mixed results for AV stimulus.
\todo[inline]{which contrast works better in which subjects?}
Individual differences when seeing a whole picture with many features vs.
serialc auditory stream of information providing incidential cues; spatial attention?

\paragraph{shortcomings of AV contrasts}
visual confounds all over the place; obvious solution: annotate frames and track
focus of attention (but gist of a frame vs. attentional focus)

@@

% spatial cues can belong to different indcategories
resembling cuts to different scene in the movie by using ``similar'' cues in the
audio-description did not work well; words are processes ``literally'' and not
``wholistically'' or put in a wider ``context'' (but Aminoff?)
%
setting\_new ist häufig vermischt mit anderer Kategorie "ein Arzt", "ein alter
Film", "auf einer Straße", "im Fernsehen", "die drei Jungs", "die zwei im Bett",
"Jenny als Teenager", "Forrest vor einem Buffet", "Kennedy", "Jenny kommt aus
dem Wohnwagen ihrer Großmutter"
% soundsscapes makes change of setting obvious before narrator kicks in
Soundscape macht es häufiger bereits vorher klar, dass Settingwechsel ist bzw.
nicht erst das annotiere Substantiv object und (room)geo ist vermischt
Retrospelinal Cortex ist in Probabilistic maps krasser als PPA.

@@

\subsection{re-use of existing data for new, independent research questions}
Due to their continuity,
complexity, and length, they offer a vast amount of data on a variety of brain
functions like low-level perception, attention, comprehension, memory, emotions,
or social interactions. This suggests the data can later be reused for variety
of totally different, independent research questions, possibly on an individual
level.

\subsection{model-driven vs. data-driven analyses}
Natural stimuli like movies \citep{hasson2008neurocinematics,
sonkusare2019naturalistic} or narratives \citep{honey2012not,
lerner2011topographic, silbert2014coupled} offer an easy to implement,
(continuous,) complex, immersive, task-free paradigm that more closely resembles
our natural dynamic environment than traditional experimental designs.

@@

\subsection*{Code availability}
% wo kommt dieser Abschnitt hin?  how to write Code availability statement
% https://www.springernature.com/gp/authors/research-data-policy/data-availability-statements/12330880
\todo[inline]{provide supporting source code, and explaining how and where
others may access all data underlying the analysis} \emph{for all studies using
    custom code in the generation or processing of datasets, a statement must be
    included here, indicating whether and how the code can be accessed,
including any restrictions to access; include information on the versions of any
software used, if relevant, and any specific variables or parameters used to
generate, test, or process the current dataset. }
